The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-19 src/ms.tex
short title
Fix "to to"

\shorttitle{Astropy Project III}
\shortauthors{The Astropy Collaboration}

@@

\author{Astropy~Collaboration}
\noaffiliation
{\let\thefootnote\relax\footnote{{
  The author list has two parts: the authors that made significant contributions
  to the writing and/or coordination of the paper (in order of contribution),
  followed by maintainers of and contributors to to the Astropy Project (in
  alphabetical order). \textbf{The position in the author list does not
  correspond to contributions to the Astropy Project as a whole.} A more
  complete list of contributors to the core package can be found in the
  \href{https://github.com/astropy/astropy/graphs/contributors}{package
  repository}, and at the \href{http://www.astropy.org/team.html}{Astropy team
  webpage}.
}}}

>>>>

\shorttitle{Astropy: Sustaining the Project and v5.0}
\shortauthors{The Astropy Collaboration}

@@

\author{Astropy~Collaboration}
\noaffiliation
{\let\thefootnote\relax\footnote{{
  The author list has two parts: the authors that made significant contributions
  to the writing and/or coordination of the paper (in order of contribution),
  followed by maintainers of and contributors to the Astropy Project (in
  alphabetical order). \textbf{The position in the author list does not
  correspond to contributions to the Astropy Project as a whole.} A more
  complete list of contributors to the core package can be found in the
  \href{https://github.com/astropy/astropy/graphs/contributors}{package
  repository}, and at the \href{http://www.astropy.org/team.html}{Astropy team
  webpage}.
}}}
